### 2017-07-28 src/4_OnlineLearning.tex
complexity of hypothesis

%=======================HASTA ACA REVISADO PROFE =========================
A learning algorithm $\mathcal{A}$ takes as input a data set $S \in
\mathscr{T}=\mathscr{P}(X\times Y)$ and selects from $\mathcal{H}$ a function
$f$ such that $f(x)\approx y $ in a predictive way:

@@

\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff \cite{dietterich2003} between three factors:
\begin{description}
\item[Complexity of the hypothesis class] for best generalisation, we should
adjust the complexity of the learner model $\hat{f}$ to the complexity of the
data $f$. The complexity of a learning problem mostly depends on the number of
training examples and the size of the searched hypothesis space. In polynomial
regression, the complexity parameter is the order of the fitted polynomial, and
therefore we need to find a way to choose the best order that minimises the
generalisation error, that is, tune the complexity of the model to best fit the
complexity of the function inherent in the data.
\item[Generalisation accuracy on new examples] is the capability of the
algorithm to generate the right output for an input instance outside the
training set. It is measured by the expected risk (equation \ref{eq:expetedrisk}).
\item[The amount of training data] in most cases, generalisation accuracy
increases as the amount of training data increases.
\end{description}

>>>>

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in
\mathscr{T}=\mathscr{P}(X\times Y)$ and selects from $\mathcal{H}$ a function
$f$ such that $f(x)\approx y $ in a predictive way:

@@

%=======================HASTA ACA REVISADO PROFE =========================
\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff between three factors \cite{dietterich2003}:
\begin{description}
\item[Complexity or capacity of the hypothesis class]

and can be measured by the Vapnik\-Chervonenkis (VC) dimension

for best generalisation, we should
adjust the complexity of the learner model $\hat{f}$ o the complexity of the
data.

In polynomial regression, the complexity parameter is the order of the fitted polynomial, and
therefore we need to find a way to choose the best order that minimises the
generalisation error, that is, tune the complexity of the model to best fit the
complexity of the function inherent in the data.

The complexity of a learning problem mostly depends on the number of
training examples and the size of the searched hypothesis space.

\item[Generalisation accuracy on new examples] is the capability of the
algorithm to generate the right output for an input instance outside the
training set. It is measured by the expected risk (equation \ref{eq:expetedrisk}).
\item[The amount of training data] in most cases, generalisation accuracy
increases as the amount of training data increases.
\end{description}
